Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-10-22 paper/ms.tex
new subsection on the SSA22 field

>>>>

\subsection{The adequacy of using SSA22 as an observational test}

{\bf The field centered on SSA22 has been known to harbor a 
  galaxy overdensity. Measurements of Lyman Break Galaxies show that
  the densest sub-field presents an overdensity 6 times the one present in a
  blank field \cite{XXX}. Using the data of \cite{Yamada2012}, we
  compute that for LAEs the whole region is only 1.4 times more dense than
  the blank fields of SXDS, SDF and GOODS-N. The densest sub-field
  in SSA22 is only 2 times denser than the average of the blank
  fields.}

{\bf This shows that the bias factor of LBGs is higher
  than LAEs. In a LCDM cosmology this implies that LAEs are, on average,
  hosted by halos less massive than those hosting LBGs. The
  interpretation of how rare is this subfield in terms of the number
  densities of dark matter halos has to assume a defined model for
  galaxy formation[...]}

{\bf Excluding the densest region in the SSA222, all the fields have a
similar number densisty as the blank fields and cannot be considered
as rare. Therefore we expect that a comparison between different
distributions for the number densities will fail at reproducing the
high density tail of the densest field in SSA22.}
